Minimizing Time Required For Graduation

### 2010-12-10 paper/paper.tex
made equation 4 actually make sense

\subsubsection{Formulation as Binary Integer Program} We can now formulate
a binary linear programming problem. Before stating the linear
program, we must first define some variables used in it: \\ \begin{itemize}
\item $ X_i = \left\{ \begin{array}{lr} 1 \text{ if we take } X_i\\ 0 \text{ if
we don't take } X_i \end{array} \right. $ \item For all $t \in O$, we let $t
= 1$.  \item Let $m = \|L\|$.  \end{itemize} We now state our problem as
follows:

\begin{equation}
    \text{Value of Quarter} = \sum_{i=1}^m Value(c_i) * X_i
    \label{qtr_val}
\end{equation}

\begin{equation}
    \sum_{i=1}^m Weight(c_i) * X_i \leq l, \forall t_j \in O,
    \label{weight_lim}
\end{equation}

\begin{equation}
    \sum_{i=1}^m t_j * X_i \leq 1, X_i \in \{0, 1\}
    \label{time_con}
\end{equation}

>>>>

\subsubsection{Formulation as Binary Integer Program} We can now formulate
a binary linear programming problem. Before stating the linear
program, we must first define some variables used in it:

\begin{itemize}
    \item $ X_i = \left\{ \begin{array}{lr} 1 \text{ if we take } X_i\\ 0 \text{ if
we don't take } X_i \end{array} \right. $ 
    \item For all $t \in O$, we let $t$ represent the conflict graph of classes
    at time period $t$.
    \item Let $m = \|L\|$.  
\end{itemize} 
We now state our problem as follows: 
Maximize:

\begin{equation}
    \text{Value of Quarter} = \sum_{i=1}^m Value(c_i) * X_i
    \label{qtr_val}
\end{equation}
Subject To:
\begin{equation}
    \sum_{i=1}^m Weight(c_i) * X_i \leq l, 
    \label{weight_lim}
\end{equation}

\begin{equation}
    \forall t \in O,X_i+X_j \leq 1, \forall pairs (X_i,X_j) \in t
    \label{time_con}
\end{equation}
